---
title: 'MIIN Part 5: Meta-analysis'
author: "Marissa Lee"
date: "January 21, 2015"
output: html_document
---

**Filename: exampleMarkdown.Rmd**  
**This markdown file does the following tasks:**  

#### Aim
Test for correlation between CWM traits and soil N effect size values. Record the outcomes in a table. In cases where the slope coefficient significantly differs from 0, plot it.

```{r globalParams, include=FALSE}
# Set global parameters

#RMarkdown caching
knitr::opts_chunk$set(cache=TRUE)

#load packages
require(ggplot2)
require(gridExtra)
require(plyr)

#source code to set up my custom ggplots theme
source('CODE/mytheme.R')

#source the custom functions that I'll be using later
source('CODE/fxn_SaveFitStats.R')
source('CODE/fxn_FitPlot.R')
source('CODE/fxn_AddPanelTitles.R')

#set default figure parameters
figuresPath<-file.path(getwd()[1], "output") #where to put the saved plots
fig.height<-2.5 #inches
fig.width<- 2.5 #inches
fig.res<-300

#read-in the dataset
dat<-read.table("DATA/DATA_SYNTHESIZED/metaDataset.txt", header=TRUE, sep="\t")

#source code that defines the order that variables appear in my figures
source('CODE/script_orderLevels.R')

#use ddply to summarize the dataset structure
summ<-ddply(dat, ~measCat+traitCat, summarize,
                 uniqueObs = length(unique(obsID)))
#summ
#head(dat)
```


### 1. Fit a random-effects model with 1 of the continuous trait variables as a fixed effect

#### A. Model syntax  

res <- rma.mv(yi, vi, mods= ~Xmod, random=list(~1 | paperID, ~1 | obsID), data=dat1, subset=measCat==MEASCAT[i], slab=paste(paperID,obsID, sep=",")) where Xmod is one of the following 12 combinations: 3 plant communities: (1) InvSpInvArea_cwm, (2) NatArea_cwm, (3) CWMDiff_cwm x 4 trait types: (1) percN, (2) litterpercN, (3) cn, (4) littercn.  Where,

**Plant community**
'InvSpInvArea_cwm' is the invasive species community weighted mean trait value; 
'NatArea_cwm' is the reference area plant community weighted mean trait value;
'CWMDiff_cwm' is the dissimilarity between the Invaded - Reference area plant community weighted mean trait value;

**Trait type**
'percN' is leaf %N;
'litterpercN' is litter %N;
'cn' is leaf C:N;
'littercn' is litter C:N;  


#### B. The mechanics of FitPlot()  

FitPlot() is a function that I made to evaluate univariate relationships between plant trait values and soil N effect sizes. For 1 plant community that you specify, this thing compares each combination of trait type (4) and soil effect measurement type (9). That means that every time I run FitPlot(), I am fitting the same model 36 times with slightly different data. 

FitPlot() needs some information to work.  It needs (1) the dataset, (2) the plant community to focus on, specified by a number 1-3, (3) the name of the column that holds information about trait data quality, and (4) the number of shades of gray to use for plotting variation in trait quality.

FitPlot() produces a list with the following objects:

- "results" : list of model fit statistics
- "data" : dataframe with the xy data used to fit the models and make the plots. This is just in case I need to quickly/painless look up info on an odd point
- "figures" : ggplot objects, one for each xy comparison
- "qual" : list of model fit statistics for an extension model I ran to evaluate the effect of trait quality... if that factor is significant then I will run into some interpretation problems

```{r fitreg, include = FALSE}

#run the model-fitting and plotting function
##### THIS WILL TAKE A LITTLE TIME, BE PATIENT ##########

# invasive species CWM trait values
INVlist<-FitPlot(dat, k=1, qualColumn='InvSpInvArea_qualRank', colorN=5)

# reference community CWM trait values
NATlist<-FitPlot(dat, k=2, qualColumn='NatArea_qualRank', colorN=5)

# dissimilarity in CWM trait values, invaded - reference communities
DIFFlist<-FitPlot(dat, k=3, qualColumn='CWMDiff_qualRank', colorN=10)

```


### 2. Save the model fit results  

Make tables and save them as new files in the output folder
```{r saveTabs, include = FALSE}

#save the model fitting results in tables
INVtab<-rbind(ldply(INVlist[['results']][['percN']]),
              ldply(INVlist[['results']][['litterpercN']]),
              ldply(INVlist[['results']][['cn']]),
              ldply(INVlist[['results']][['littercn']]))[,-1]
NATtab<-rbind(ldply(NATlist[['results']][['percN']]),
              ldply(NATlist[['results']][['litterpercN']]),
              ldply(NATlist[['results']][['cn']]),
              ldply(NATlist[['results']][['littercn']]))[,-1]
DIFFtab<-rbind(ldply(DIFFlist[['results']][['percN']]),
              ldply(DIFFlist[['results']][['litterpercN']]),
              ldply(DIFFlist[['results']][['cn']]),
              ldply(DIFFlist[['results']][['littercn']]))[,-1]

#save those tables as new files
newfilename<-'INVtab.txt'
write.table(INVtab, file=paste(figuresPath,'allRegressionTables',newfilename, sep='/'), sep='\t', row.names=FALSE)
newfilename<-'NATtab.txt'
write.table(NATtab, file=paste(figuresPath,'allRegressionTables',newfilename, sep='/'), sep='\t', row.names=FALSE)
newfilename<-'DIFFtab.txt'
write.table(DIFFtab, file=paste(figuresPath,'allRegressionTables',newfilename, sep='/'), sep='\t', row.names=FALSE)

```



### 3. Produce all possible plots and save them  

Loop through all plots (3 plant communities x 4 trait types x 9 soil N effects = 108 comparisons). Each figure has data for 1 plant community x trait type with 9 scatterplot panels for each soil N effect size  

```{r plotregAll, include = FALSE}

#plot notes:
#predicted values calculated based on only the fixed effects
#ci = 95% confidence interval on the fixed effect coefficients

#add panel labels
INVlist1<-AddPanelTitles(INVlist)
NATlist1<-AddPanelTitles(NATlist)
DIFFlist1<-AddPanelTitles(DIFFlist)

#plot and save
##### THIS WILL TAKE A LITTLE TIME, BE PATIENT ##########
PLANTlist<-list(INVlist1, NATlist1, DIFFlist1)
PLANTlabel<-c('INV','NAT','DIFF')
xlabel.PlantText<-c('Invasive species','Reference area','Invaded - Reference area')
xlabel.TraitText<-c('Leaf %N','Litter %N','Leaf C:N','Litter C:N')
l<-0
for(l in 1:length(PLANTlist)){
  i<-0
  for (i in 1:length(TRAIT)){
    CURRTRAIT<-PLANTlist[[l]][[i]]
    xlabel<- textGrob(paste(xlabel.PlantText[l],xlabel.TraitText[i], sep=", "), x=0.5,
                      y=unit(1,'lines'))
    
    #open image file connection
    newfilename<-paste(paste(PLANTlabel[l],TRAIT[i], sep="_"),'.pdf',sep="")
    pdf(paste(figuresPath,'allRegressionPlots',newfilename, sep='/'), 
        width = fig.width*3.5, height = fig.height*3.5)

    grid.arrange(
      textGrob('Std. Mean Diff. (Inv-Ref)', y=0.5,x=unit(1,'lines'), rot=90), # ylabel topleft
      do.call(arrangeGrob,  CURRTRAIT),
      textGrob(" "), #bottom left
      xlabel, #bottom right
      widths = unit.c(unit(2.5, "lines"), unit(1, "npc") - unit(2.5, "lines")), 
      heights = unit.c(unit(1, "npc") - unit(2.5, "lines"), unit(2.5, "lines")), 
      nrow=2, ncol=2
    )
    
    dev.off()
    
  }
}

```


### 4. Pull out the signifiant plots and make publishable figures

**Invasive species traits**
```{r plotreg_inv, include = FALSE}

#identify the significant relationships
INVtab[INVtab$pVal <0.1 & INVtab$measType %in% MEASCAT,]

#plot and save
newfilename<-"INVreg.pdf"
pdf(paste(figuresPath,newfilename, sep='/'), width = fig.width, height = fig.height)
INVlist[['figures']][['percN']][['soiln']] + 
    xlab('Invasive sp. Leaf %N') + ylab('Soil N effect size')
dev.off()

```


**Reference traits** -- No significant plots
```{r plotreg_ref, include = FALSE}

#identify significant relationships
NATtab[NATtab$pVal <0.1 & NATtab$measType %in% MEASCAT,]

```


**Trait dissimilarity, invaded minus reference area**
```{r plotreg_diff, include = FALSE}

#identify significant relationships
DIFFtab[DIFFtab$pVal <0.1 & DIFFtab$measType %in% MEASCAT,]

#plot and save
newfilename<-"DIFFreg.pdf"
pdf(paste(figuresPath,newfilename, sep='/'), width = fig.width*2, height = fig.height*2)
grid.arrange(

  DIFFlist[['figures']][['litterpercN']][['toti']] + 
    xlab('Inv.-Ref. CWM litter %N') + ylab('Total inorg. N effect size') + ggtitle('a'),

  DIFFlist[['figures']][['littercn']][['toti']] + 
    xlab('Inv.-Ref. CWM litter C:N') + ylab('Total inorg. N effect size') + ggtitle('b'),

  DIFFlist[['figures']][['cn']][['nminz']] + 
    xlab('Inv.-Ref. CWM leaf C:N') + ylab('Mineralization effect size') + ggtitle('c'),
  
  DIFFlist[['figures']][['cn']][['soilcn']] + 
    xlab('Inv.-Ref. CWM leaf C:N') + ylab('Soil C:N effect size') + ggtitle('d'),
  ncol=2
)
dev.off()

```



